|

### 2021-03-14 appendix/appendix.Rmd
adding funnel plots

@@

@@

@@

1.  The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10% confidence level.**
3.  The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

@@

@@

@@

@@

@@

@@

@@

1.  The results are highly heterogeneous: \$I\^2 = \$ `r round(mod$I2*100, 2)`.
2.  The estimated SMD in the random effects model is \$g = \$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10% confidence level.**
3.  The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

@@

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

>>>>

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on per capita government expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of per capita expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on log of per capita government expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

1.  The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10% confidence level.**
3.  The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(eggers.test(mod)$p<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log of lower houses size (logN) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

1.  The results are highly heterogeneous: \$I\^2 = \$ `r round(mod$I2*100, 2)`.
2.  The estimated SMD in the random effects model is \$g = \$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10% confidence level.**
3.  The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(eggers.test(mod)$p<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.

@@

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on the public expenditure share of GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```

@@

```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
funnel(mod, contour = c(.95,.975,.99),
       col.contour=c("darkblue","blue","lightblue"))
legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
       fill=c("darkblue","blue","lightblue"))
```
